### 2014-11-06 contract-language.tex
edits
Commiting appendix

  \vspace{-1em}
  \begin{smathpar}
  \ecc = \forall a,b. ~\hbo{a}{b} \wedge \vis{b}{\cureff} \Rightarrow \vis{a}{\cureff}
  \end{smathpar}

@@

  \vspace{-1em}
  \begin{smathpar}
  \ccc = \forall a.~\hbo{a}{\cureff} \Rightarrow \vis{a}{\cureff}
  \end{smathpar}

@@

  \vspace{-1em}
  \begin{smathpar}
  \scc = \forall a.~\sameobj{a}{\cureff} \Rightarrow \vis{a}{\cureff} ~\vee~ \vis{\cureff}{a} ~\vee~ a = \cureff
  \end{smathpar}

@@

\begin{theorem}[Soundness of Contract Enforcement]
\label{lem:core-preservation}
Let $\cv$ be a well-formed contract of a replicated data type operation
$\mathit{op}$, and let $\tau$ denote the consistency class of $\cv$ as
determined by the contract classification scheme. For all well-formed execution
states $\E$, $\E'$ such that
$\auxred{} {\E,\langle op,\tau \rangle;\sigma \pll \Sigma} {\eff} {\E', \sigma
\pll \Sigma}$, if $\E' \models \cv_\tau[\eff/\cureff]$, then $\E' \models
\cv[\eff/\cureff]$
\end{theorem}

>>>>

  \vspace{-1.5em}
  \begin{smathpar}
  \ecc = \forall a,b. ~\hbo{a}{b} \wedge \vis{b}{\cureff} \Rightarrow \vis{a}{\cureff}
  \end{smathpar}

@@

  \vspace{-1.5em}
  \begin{smathpar}
  \ccc = \forall a.~\hbo{a}{\cureff} \Rightarrow \vis{a}{\cureff}
  \end{smathpar}

@@

  \vspace{-1.5em}
  \begin{smathpar}
  \scc = \forall a.~\sameobj{a}{\cureff} \Rightarrow \vis{a}{\cureff} ~\vee~ \vis{\cureff}{a} ~\vee~ a = \cureff
  \end{smathpar}

@@

\begin{theorem}[Soundness of Contract Enforcement]
\label{thm:classification-sound}
Let $\cv$ be a well-formed contract of a replicated data type operation
$\mathit{op}$, and let $\tau$ denote the consistency class of $\cv$ as
determined by the contract classification scheme. For all well-formed execution
states $\E$, $\E'$ such that
$\auxred{} {\E,\langle op,\tau \rangle;\sigma \pll \Sigma} {\eff} {\E', \sigma
\pll \Sigma}$, if $\E' \models \cv_\tau[\eff/\cureff]$, then $\E' \models
\cv[\eff/\cureff]$
\end{theorem}
